
#1
---
title: "Assesment-1.1"
author: "Ozan Aksut s4658715"
date: "01/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#2
# RMarkdown editing (Part 1)

#3 & 4
### Analyze. Share. Reproduce.
### Your data tells a story. 
* Tell it with R Markdown.* 
**Turn your analyses into high quality** *documents, reports, presentations and dashboards.*


#5
[Rmarkdown](https://rmarkdown.rstudio.com/lesson-8.html)

```{r}
library(tidyverse)
library(skimr)
library(janitor)
```

#6
```{r}
fastfood <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
data %>% head(10)

```

#7
```{r}
knitr::kable(head(fastfood[1:5, 1:5]), "pipe")
```

#8
```{r}
fastfood %>%
filter(calories>1000)

```

#9
```{r}
fastfood %>%
 filter(total_fat>40 & total_carb>80)
```

```{r}
dont_eat_this <- fastfood %>%
   filter(total_fat>40 & total_carb>80)
```

#10
```{r}
mcdonalds <- fastfood %>% 
  filter(restaurant == "Mcdonalds")
```



#Part 2

#11
```{r}
skim(fastfood)
```

#12
```{r}
fastfood %>%
count(restaurant)
```

#13
```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean(calories))
```

#14
```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_callories=mean(calories))
```

#15
```{r}
library(ggplot2)
```

```{r}
ggplot(fastfood, aes(x = restaurant, y = total_fat)) +
geom_point(colour = "blue")
```

#The display of data or information in a graph, chart, or other visual format is known as data visualisation. It uses pictures to convey data connections. This is significant since it makes it easier to see trends and patterns.

#16
```{r}
max_total_fat <- fastfood %>%
  group_by(restaurant) %>%
  summarise(max_total_fat=max(total_fat))
```


#17
```{r}
ggplot(mcdonalds, aes(x = sugar, y = protein)) +
  geom_point(color = "green")
```

# Part 3

#18
```{r}
str(fastfood)
```

```{r}
fastfood$restaurant <- as.factor(fastfood$restaurant)
```

#19
```{r}
calories_type <- cut_number(fastfood$calories, n = 3,labels=c("low", "med", "high"))
```

```{r}
fastfood <- fastfood%>%
mutate(calories_type = cut_number(fastfood$calories, n = 3,labels=c("low", "med", "high")))

```

#20
```{r}
fastfood %>%
  count(restaurant, calories_type, sort = TRUE) %>%
  ggplot(aes(restaurant, n, fill = calories_type)) +
  geom_col() +
  facet_wrap(calories_type~.)+
  coord_flip() +
  labs(x = "Restaurant Names", y = "Number of Restaurant", title = "Calories type for each restaurant", caption = "Image 1: Bar Graph") +
  theme_test()
```

#21
```{r}
fastfood <-fastfood%>%
group_by(restaurant) %>%
  mutate(trans_fat_percent = trans_fat/total_fat * 10) %>%
  relocate(trans_fat_percent, .after = restaurant)
```


#22
```{r}
fastfood %>% 
ggplot(aes(restaurant, trans_fat, color = restaurant)) +
  geom_violin() +
  labs(x = "Restaurant Names", y = "Amount of Trans Fat", title = "Trans fat for each type of restaurant " ) +
  theme_classic()

```


#23
```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(total_fat=mean(total_fat))

```


#24

```{r}
ggplot(fastfood, aes(restaurant, total_fat, color = total_fat)) +
  geom_jitter()+
  labs(x = "Restaurant Names", y = "Amount of Total Fat", title = "Total fat for each type of restaurant " ) 
  
```








































